\nonumchap{Acknowledgements}
    %
First and foremost, I thank my supervisors Elia Bruni and Dieuwke Hupkes. The amount of heart and time they put into this project is overwhelming and I could not have completed it without their constant support, motivation, and feedbacks. I am grateful to them for hearing out my ideas and encouraging me to pursue them in a structured way. I thank them for the engagements and meetings with the researchers at FAIR, Paris, for the regular idea exchange meetings with other graduate students, which was an extremely helpful platform for discussing new idea \& getting feedback on my work and for the exposure to research in general that I received during the course of the thesis.

I would like to especially thank Kris Korrel who worked with me extensively on this project and is taking it further in even more interesting directions. I have rarely met someone with such an effortless approach to programming and I am grateful to him for helping me out whenever I got stuck on the coding part. I had some amazing technical discussions during the course of my thesis with Aashish Venkatesh and Yann Dubois, which have definitely broadened my outlook towards research and given me amazing new ideas to ponder on. I thank them for this and wish them all the best for their next endeavors.

Finally I would like to thank my girlfriend Pallavi for being my rock and for all her love and support, my family for their constant encouragement and the most amazing Aviral for always cheering me up. 


    % signature containing place, name and date
    \signature
